Predictions of Occupied Beds at Faculties Providing Daily Shelter And/Or Overnight Services Using Multivariate Linear Regression Leads To Possible Maximized Efficiency of Government Investment To These Faculties

### 2024-12-04 paper/paper.qmd
Fixes one more mistake in title

---
title: "Predictions of Occupied Beds at Faculties Providing Daily Shelter And/Or Overnight Services Using Multivariate Linear Regression Leads To Possible Maximized Efficient of Government Investment To These Faculties"
author: 
  - Kevn Shao
thanks: "Code and data are available at: https://github.com/KevinShao1357/Toronto_Daily_Shelter_And_Overnight_Service_Modelling.git."
date: today
date-format: long
abstract: "Recently, the Canadian government expresses interest in continuous investment in government faculties providing daily shelter and/or overnight services. With the aim to evaluate the validity of predicting the occupied beds at a related faculties at a day, which can reflect the demand of such services at such locations, a multivariate linear regression model is constructed, with the city to Downtown Toronto, and the gender and age set to Mixed Adults. Five predictor variables are used, including two numerical variables, occupancy rate and capacity, and three categorical variables, including classification, service types, and program types. The final results showed a possible violation of linearity assumptions such as homoscedasticity and normality of errors, but also reflects the possibility of predicting the appropriate amount of investment to these facilities using this statistical approach."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Predictions of Occupied Beds at Faculties Providing Daily Shelter And/Or Overnight Services Using Multivariate Linear Regression Leads To Possible Maximized Efficiency of Government Investment To These Faculties"
author: 
  - Kevn Shao
thanks: "Code and data are available at: https://github.com/KevinShao1357/Toronto_Daily_Shelter_And_Overnight_Service_Modelling.git."
date: today
date-format: long
abstract: "Recently, the Canadian government expresses interest in continuous investment in government faculties providing daily shelter and/or overnight services. With the aim to evaluate the validity of predicting the occupied beds at a related faculties at a day, which can reflect the demand of such services at such locations, a multivariate linear regression model is constructed, with the city to Downtown Toronto, and the gender and age set to Mixed Adults. Five predictor variables are used, including two numerical variables, occupancy rate and capacity, and three categorical variables, including classification, service types, and program types. The final results showed a possible violation of linearity assumptions such as homoscedasticity and normality of errors, but also reflects the possibility of predicting the appropriate amount of investment to these facilities using this statistical approach."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
